A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}

@@

>>>>

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{float}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm]{appsbench.pdf}
  \caption{Prcentage of overall improvements in some real-world Python applications. Nearly none of the applications performed worse. Python Pickle and html5lib faster around \%3 to \%4. }
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm]{slowpickle.png}
  \caption{Python Pickle module benchmark. Minimum Iteration: changed from 0.705s to 0.681s: 1.04 times faster. Average iteration: changed from 0.710s to 0.686s: 1.04 times faster. Standard deviation of new implementation 2.0383 times smaller}
\end{figure}
